### 2024-01-21 outputs/paper/paper.qmd
download the data, do the reference, and some introduction and data parts

---
title: "Analysis of Major Crimes in Toronto And Suggestions on How to Protect Ourselves"
author: "Boxuan Yi"
date: 20 January 2024
abstract: "Safety is one of the most important factors that people consider when deciding where to live and go. This report uses data from Open Data Toronto to analyze the occurrences of various types of crimes in different regions of Toronto, as well as the trend over the past ten years. The result shows that Downtown Toronto and evenings have a relatively high occurrences of crimes, which could be used as a suggestion on both individuals and government dicision-making."
format: pdf
bibliography: references.bib
---
## Introduction
On Dec 25th, 2023, the Christmas Day, a news has raised huge concerns among people — a man was seriously injured after stabbing in downtown Toronto. This was not the first such incident on that block in December; unfortunately, such distressing news has become more and more prevalent nowadays. As the pandemic comes to an end, there is a noticeable increase in people returning to the office and going out more frequently than in previous years. Naturally, public safety has become particularly crucial, prompting a crucial question: How can we proactively prevent such incidents from affecting ourselves and our loved ones?

Providing information like location and crime types, major crimes statistics is an important tool for resource allocation and law enforcement strategy. It also provides the public a clear picture of the safety, which helps individuals make informed decisions, influence choices such as where to buy a house.

For this paper, I will use open-access data from the OpenDataToronto [@rOpenDataToronto] to analyze major crime patterns over the years and how ordinary citizens could do to reduce the likelihood of getting hurt. In addition, I will discuss how funding could be allocated for higher efficiency and potential bias in crime data. In this paper, I discuss the data in Section 2, including data source and software (Section 2.1), data collection (Section 2.2), data analysis and visualizations (Section 2.3). In Section 3, I conclude that….

```{r}
#| message: false
#| echo: false
# Load packages
library(opendatatoronto)
library(janitor)
library(tidyverse)
library(leaflet)
library(dplyr)
library(here)
library(knitr)
```

```{r}
#| message: false
#| echo: false
clean_mci_data <- read_csv(
    file = here("inputs/data/clean_mci.csv"))
```

```{r}
#| include: false
# Test
clean_mci_data$report_year |> min() == 2014
clean_mci_data$report_year |> max() == 2023
clean_mci_data$occ_year |> unique()
any(duplicated(clean_mci_data$x_id))

clean_mci_data$mci_category |> unique() == c("Assault", "Robbery", "Auto Theft", "Break and Enter", "Theft Over")
clean_mci_data$division |> unique()
clean_mci_data$occ_dow |> unique()
clean_mci_data$occ_hour |> class() == "numeric"
```

## Data
### Data Source and Software
The data utilized throughout this paper, in csv format, is obtained from Toronto Police Services on the City of Toronto Open Data Website [@rOpenDataToronto], with the title “MAJOR CRIME INDICATORS”.

This dataset will be processed and analyzed in the open source R [@r] using packages Dplyr [@rDplyr], Tidyverse [@rTidyverse], Here [@rHere], Leaflet [@rLeaflet], and Janitor [@rJanitor]. Visualizations including tables and figures will be created using ggplot2 [@rGgplot2] and Knitr[@Knitr].

### Data Collection
The dataset contains all Major Crime Indicators occurrences by report data. The categories of major crimes are Assault, Break and Enter, Auto Theft, Robbery and Theft Over. The latest refresh was on Jan 11, 2024.

There are two factors that may influence the reliability of the data. First, this dataset includes all occurrences reported to the Toronto Police Station, except those have been considered as unfounded. Second, this data is provided at the offence and victim level, so one occurrence number may have a few rows of data with different major crime indicators types used to categorize the occurrence.

### Data Analysis and Visualizations

```{r}
#| message: false
#| echo: false
#| label: tbl-clean_mci_data
#| tbl-cap: The Number of Major Crimes and the Month with the Most Crimes (2014-2023)
# Create a table with year, 2014 to 2023, the number of crimes in each year, and the month with the most crimes correspondingly.
clean_mci_data |>
  filter(occ_year >= 2014) |>
  group_by(occ_year, occ_month) |>
  summarise(n = n()) |>
  group_by(occ_year) |>
  summarise(
    total_number_of_crimes = sum(n),
    the_most_frequent_month = occ_month[which.max(n)]
  ) |>
  distinct(occ_year, .keep_all = TRUE) |>
  select(occ_year, total_number_of_crimes, the_most_frequent_month) |> 
  kable(
    col.names = c("Year", "Total Number of Crimes", "Month with the Most Crimes"),
    booktabs = TRUE
  )
```

```{r}
#| message: false
#| echo: false
#| label: fig-types_of_crimes
#| fig-cap: The Number of Crimes Reported, Classified by Crime Types (2014-2023)
clean_mci_data |>
  ggplot(mapping = aes(x = factor(report_year), fill = mci_category)) +
  geom_bar(position = "stack", stat = "count") +
  labs(x = "Year", y = "Total Number of Crimes", fill = "Types of Major Crimes") +
  theme(legend.position = "right") +
  scale_fill_brewer(palette = "Set3")
```

```{r}
#| include: false
clean_mci_data <- clean_mci_data |>
  mutate(
    division_area =
      case_match(
        division,
        "D43" ~ "Scarborough",
        "D42" ~ "Scarborough",
        "D41" ~ "Scarborough",
        "D53" ~ "Toronto-East York",
        "D55" ~ "Toronto-East York",
        "D52" ~ "Toronto-East York",
        "D51" ~ "Toronto-East York",
        "D54" ~ "Toronto-East York",
        "D32" ~ "North York",
        "D33" ~ "North York",
        "D31" ~ "North York",
        "D22" ~ "Etobicoke",
        "D23" ~ "Etobicoke",
        "D14" ~ "Etobicoke-York",
        "D11" ~ "Etobicoke-York",
        "D12" ~ "Etobicoke-York",
        "D13" ~ "Etobicoke-York",
        "NSA" ~ "Other"))
```

```{r}
#| include: false
clean_mci_data <- clean_mci_data |> 
  mutate(
    weekday_weekend =
      case_match(
        occ_dow,
        "Wednesday" ~ "Weekday",
        "Tuesday" ~ "Weekday",
        "Thursday" ~ "Weekday",
        "Sunday" ~ "Weekend",
        "Monday" ~ "Weekday",
        "Friday" ~ "Weekday",
        "Saturday" ~ "Weekend",
        "" ~ "Other"))
head(clean_mci_data)
```

```{r}
#| message: false
#| echo: false
#| label: fig-area_of_crimes
#| fig-cap: Total Number of Crimes in Different Police Division Areas
clean_mci_data |>
  filter(occ_year >= 2014) |>
  count(occ_year, division_area) |>
  ggplot(aes(x = occ_year, y = n, color = division_area)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method = lm, se = FALSE) +
  labs(x = "Year",
       y = "Total Number of Crimes",
       color = "Division Area")
```

```{r}
#| message: false
#| echo: false
#| label: fig-time_of_crimes
#| fig-cap: Number of Crimes in a Day
clean_mci_data |>
  filter(weekday_weekend == 'Weekday' | weekday_weekend == 'Weekend') |>
  count(occ_hour, weekday_weekend) |>
  ggplot(mapping = aes(x = occ_hour, y = n, color = weekday_weekend)) +
  geom_line() +
  theme(legend.position = "top") +
  labs(x = "Time In a Day", y = "Number of Crimes", color = "Weekday or Weekend") +
  scale_color_manual(values = c("Weekday" = "steelblue3", "Weekend" = "indianred3"))
```

## Conclusion
In summary,

\newpage

## References

### 2024-01-21 scripts/00-simulated_data.qmd
download the data, do the reference, and some introduction and data parts

---
title: "Simulated Data for the Analysis of Major Crimes in Toronto"
author: "Boxuan Yi"
format: html
---

```{r}
#### Preamble ####
# Purpose: Simulate the dataset of major crimes in Toronto
# Author: Boxuan Yi
# Email: boxuan.yi@mail.utoronto.ca
# Date: 17 January 2024
```

### 2024-01-21 scripts/01-download_data.qmd
download the data, do the reference, and some introduction and data parts

---
title: "Download and Save the Actual Data on MCI"
author: "Boxuan Yi"
format: html
---

```{r}
#### Preamble ####
# Purpose: Download and save the actual data on major crimes that reported in Toronto 
# from 2014 to 2023
# Author: Boxuan Yi
# Email: boxuan.yi@mail.utoronto.ca
# Date: 18 January 2024
# Prerequisites: Know where to get major crimes data.
# I will use MCI as an abbreviation of Major Crime Indicator
```

```{r}
# Install all the packages I need for this analysis
install.packages('opendatatoronto')
install.packages('dplyr')
install.packages('tidyverse')
install.packages('janitor')
install.packages('leaflet')
install.packages('knitr')
install.packages('here')
```

```{r}
library(opendatatoronto)
library(dplyr)
library(tidyverse)
library(here)
library(janitor)
```

```{r}
# get package and all resources for this package
package <- show_package("major-crime-indicators")
resources <- list_package_resources("major-crime-indicators")

# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))

# load the second one
raw_mci_data <- filter(datastore_resources, row_number()==2) %>% get_resource()
```

```{r}
# Write data
write_csv (
  x = raw_mci_data,
  file = "unedited_data.csv"
)
```

```{r}
# Read and clean the dataset
raw_mci_data <- read_csv(
    file = here("inputs/data/unedited_data.csv"))
clean_mci_data <- clean_names(raw_mci_data)
```

```{r}
# Write the cleaned dataset
write_csv (
  x = clean_mci_data,
  file = "clean_mci.csv"
)
```

```{r}
clean_mci_data <- read_csv(
    file = here("inputs/data/clean_mci.csv"))
```

### 2024-01-21 outputs/paper/paper.qmd
figure explanation corrected

@@
 library(dplyr)
+library(ggplot2)
 library(here)
@@
 ## Data
+
 ### Data Source and Software
@@
 ### Data Analysis and Visualizations
+The Major Crimes in Toronto dataset contains 27 columns and 372899 rows, including the repeated occurrences with different crime categories.
+All the samples of major crimes were reported from 2014 to 2023.
+Among 27 columns, the variables I will use are x_id, report_year, occ_year, occ_month, occ_dow (Day of the Week Offence Occurred), occ_hour, mci_category, division.
+I will create two more variables, division_area, which classifies 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA), and weekend_weekday, which indicates whether the occurrence happen on a weekday or a weekend.
 
@@
 ```
+Table 1 provides a brief summary of the total number of crimes from 2014 to 2023.
+Over this period, the overall number of crimes shows a consistent increase, except for the years 2020 and 2021, which have a decline probably due to the impact of the pandemic.
+However, in 2022 and 2023, there is a significant increase by more than 6000.
+In each year, the month with the highest number of crimes tends to be either July, August, or October, concentrating primarily in the summer-fall period.
 
@@
 ```
+Figure 1 visualizes the annual distribution of major crime types with five categories: Assault, Break and Enter, Auto Theft, Robbery, and Theft Over.
+Across all years, 'Assault' records the highest count, followed by 'Break and Enter' and 'Auto Theft'.
+'Robbery' and 'Theft Over' show comparatively lower numbers.
+Notably, there has been a slight decrease in “Break and Enter” since the pandemic, and an obvious increase in 'Auto Theft' during 2022 and 2023, leading ‘Auto Theft’ surpassing the number of 'Break and Enter’.
 
@@
         "" ~ "Other"))
-head(clean_mci_data)
+clean_mci_data
 ```
@@
 ```
+There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
+Putting them into 6 regions based on geographical location, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other for NSA.
+Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
+North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
+
+Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
+North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
 
@@
 ```
+Figure 3 indicates the preferred time for committing crimes.
+The graph reveals a higher likelihood of criminal behaviors during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning.
+Interestingly, there is a surprising local peak at noon, while 11:00 and 13:00 do not show a high probability.
 

### 2024-01-21 scripts/01-download_data.qmd
figure explanation corrected

@@
 install.packages('leaflet')
+install.packages('ggplot2')
 install.packages('knitr')

### 2024-01-23 outputs/paper/paper.qmd
found some typo and create another table

@@
 abstract: "Safety is one of the most important factors that people consider when deciding where to live and go.
-This report uses data from Open Data Toronto to analyze the occurrences of various types of crimes in different regions of Toronto, as well as the trend over the past ten years.
-The result shows that Downtown Toronto and evenings have a relatively high occurrences of crimes, which could be used as a suggestion on both individuals and government dicision-making."
+This report uses data from Open Data Toronto to analyze the occurrences of various types of crimes in different regions and time of Toronto, as well as the trend over the past ten years.
+The result shows that Downtown Toronto and evenings & noon have a relatively high occurrences of crimes, which could be used as a suggestion on both individual and government dicision-making."
 format: pdf
@@
 As the pandemic comes to an end, there is a noticeable increase in people returning to the office and going out more frequently than in previous years.
-Naturally, public safety has become particularly crucial, prompting a crucial question: How can we proactively prevent such incidents from affecting ourselves and our loved ones?
+Naturally, public safety and private security have become particularly crucial, leading to a significant question: How can we proactively prevent such incidents from affecting ourselves and our loved ones?
 
-Providing information like location and crime types, major crimes statistics is an important tool for resource allocation and law enforcement strategy.
-It also provides the public a clear picture of the safety, which helps individuals make informed decisions, influence choices such as where to buy a house.
+Major crimes statistics is an important tool for resource allocation and law enforcement strategy.
+It also provides the public a clear picture of the safety and helps individuals make informed decisions, influencing choices such as when to go out and where to buy a house.
+For this paper, I will use open-access data, titled ‘Major Crime Indicator’ from the OpenDataToronto [@rOpenDataToronto] to analyze the distribution of major crimes—classified as Assault, Break and Enter, Auto Theft, Robbery, and Theft Over—over the past ten years.
+My analysis will also delve into practical actions ordinary citizens and the government can do to enhance safety and efficiency.
 
-For this paper, I will use open-access data from the OpenDataToronto [@rOpenDataToronto] to analyze major crime patterns over the years and how ordinary citizens could do to reduce the likelihood of getting hurt.
-In addition, I will discuss how funding could be allocated for higher efficiency and potential bias in crime data.
 In this paper, I discuss the data in Section 2, including data source and software (Section 2.1), data collection (Section 2.2), data analysis and visualizations (Section 2.3).
-In Section 3, I conclude that….
+In Section 3, I conclude that Toronto-East York & evening and noon experience the highest numbers of crimes.
+Among the five major crime categories as mentioned, 'Assault' records the highest count, with 'Break and Enter' and 'Auto Theft' following closely.
 
@@
 #| include: false
+# Explore
 # Test
@@
 ### Data Source and Software
-The data utilized throughout this paper, in csv format, is obtained from Toronto Police Services on the City of Toronto Open Data Website [@rOpenDataToronto], with the title “MAJOR CRIME INDICATORS”.
+The data utilized throughout this paper, in csv format, was obtained from Toronto Police Services on the City of Toronto Open Data Website [@rOpenDataToronto], with the title “MAJOR CRIME INDICATORS”.
 
-This dataset will be processed and analyzed in the open source R [@r] using packages Dplyr [@rDplyr], Tidyverse [@rTidyverse], Here [@rHere], Leaflet [@rLeaflet], and Janitor [@rJanitor].
+The dataset will be processed and analyzed in R [@r] using packages Dplyr [@rDplyr], Tidyverse [@rTidyverse], Here [@rHere], Leaflet [@rLeaflet], and Janitor [@rJanitor].
 Visualizations including tables and figures will be created using ggplot2 [@rGgplot2] and Knitr[@Knitr].
@@
 ```
+Factors contributing to this uptrend are multifaceted, ranging from societal shifts associated with the pandemic to economic uncertainties.
+In particular, I will discuss the distribution of crimes from three aspects: types of crime, regions and time in a day.
+
 Figure 1 visualizes the annual distribution of major crime types with five categories: Assault, Break and Enter, Auto Theft, Robbery, and Theft Over.
@@
 ```
+There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
+I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other.
+```{r}
+#| message: false
+#| echo: false
+#| label: tbl-division_area
+#| tbl-cap: Police divisions in 6 areas(including other)
+
+clean_mci_data%>%
+  group_by(division_area) %>%
+  summarise(division = toString(unique(division))) |> kable()
+
+```
 
@@
 ```
-There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
-Putting them into 6 regions based on geographical location, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other for NSA.
-Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
-North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
 
@@
 ```
-Figure 3 indicates the preferred time for committing crimes.
-The graph reveals a higher likelihood of criminal behaviors during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning.
+Figure 3 indicates the preferred time to commit crimes.
+The graph reveals a higher likelihood of criminal behaviours during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning.
 Interestingly, there is a surprising local peak at noon, while 11:00 and 13:00 do not show a high probability.
 
+```{r}
+# Share
+```
+
 ## Conclusion
-In summary,
+In summary, ‘Assault’ has always ranked as the most common major crime over the past ten years.
+However, the difference between ‘Auto Theft’ and ‘Assault’ is shrinking, as the number of ‘Auto Theft’ is increasing rapidly.
+There need be more safety actions on automobiles, and people should lock the doors and not leave any packages visible through car windows to improve automobile security.
+Due to the difficulty to prove ‘Assault’ as a crime, installing cameras at the front door or home security systems is a good idea to provide evidence for ‘Assault’, while it can also record suspicious individuals and vehicles near one's residence.
+Taking proactive steps, such as responding to knocks cautiously while keeping the door locked, and refraining from touching anything until the police have inspected, is crucial for personal safety and should be instilled in children as well.
+
+The Toronto-East York region reports the highest number of crimes, with North York, Scarborough, and Etobicoke-York following.
+Resources and fundings allocation should have an emphasis on Toronto-East York, especially the downtown area, considering the amount of people coming to work despite not residing there.
+
+Focus on safety during midnight and noon hours is important too.
+The most common time for a crime occurrence include noon and midnight, especially between 6:00 PM to 8:00 PM.
+In order to prevent such incidents, people who work from home but go out for lunch, as well as those with children returning home for lunch around noon, should keep their ears and eyes open for suspicious surroundings.
+Evening hours in any region also need more cautions from residents and security from the government.
+
+It is crucial to recognize that, though Toronto-East York records the most crimes, it also has the largest number of residents.
+Therefore, it could be biased to claim that Toronto-East York has the highest crime rate, or North York is getting dangerous, as North York has witnessed a growing population in recent years.
+Moreover, when creating this dataset, one occurrence number may have a few rows with different major crime indicators types used to categorize the occurrence.
+Therefore, some incidents of 'Auto Theft,' 'Robbery,' and 'Theft Over' may be potentially recorded multiple times under 'Break and Enter.' Consequently, the number of crimes classified as just ‘Break and Enter’ is overestimated, the actual number may be lower than what is shown now in the dataset.
 

### 2024-01-23 scripts/00-simulated_data.qmd
Do the plan and simulation

@@
 author: "Boxuan Yi"
-format: html
+format: pdf
 ---
@@
 ```{r}
+#| message: false
+#| echo: false
 #### Preamble ####
@@
 ```
+
+```{r}
+#| message: false
+#| echo: false
+# Plan
+library(tidyverse)
+library(janitor)
+
+```
+
+# Plan
+![Plan Image](project/scripts/plan.png)
+
+```{r}
+# Simulate
+#| message: false
+#| echo: false
+# Simulation for the number of crimes in each year (2014-2023) and the month with the most crimes in each year
+set.seed(7)
+
+months <- c("January", "February", "March", "April", "May", "June", "July",
+            "August", "September", "October", "November", "December")
+
+simulated_data1 <-
+  tibble(
+    "Year" = 2014:2023,
+    "Number of Crimes" = runif(n = 10, min = 0, max = 10000),
+    "Month" = sample(months, 10, replace = TRUE)
+    )
+simulated_data1
+
+```
+
+```{r}
+#| message: false
+#| echo: false
+# Simulation for the number of crimes classified in major crime types
+set.seed(7)
+
+simulated_data2 <-
+  tibble(
+    "Year" = 2014:2023,
+    "Number of Assault" = runif(n = 10, min = 0, max = 2000),
+    "Number of Auto Theft" = runif(n = 10, min = 0, max = 2000),
+    "Number of Break and Enter" = runif(n = 10, min = 0, max = 2000),
+    "Number of Robbery" = runif(n = 10, min = 0, max = 2000),
+    "Number of Theft Over" = runif(n = 10, min = 0, max = 2000)
+    )
+simulated_data2
+
+```
+
+```{r}
+#| message: false
+#| echo: false
+# Simulation for the number of crimes classified in major crime types
+set.seed(7)
+simulated_data3 <-
+  tibble(
+    "Year" = 2014:2023,
+    "Etobicoke" = runif(n = 10, min = 0, max = 1000),
+    "Etobicoke-York" = runif(n = 10, min = 0, max = 1000),
+    "North York" = runif(n = 10, min = 0, max = 1000),
+    "Other" = runif(n = 10, min = 0, max = 1000),
+    "Scarborough" = runif(n = 10, min = 0, max = 1000),
+    "Toronto-East York" = runif(n = 10, min = 0, max = 1000)
+    )
+simulated_data3
+```
+
+```{r}
+#| message: false
+#| echo: false
+# Simulation for the number of crimes classified in major crime types
+set.seed(7)
+simulated_data4 <-
+  tibble(
+    "Hour" = 0:23,
+    "Etobicoke" = runif(n = 24, min = 0, max = 1000),
+    )
+simulated_data4
+```

### 2024-01-23 outputs/paper/paper.qmd
finish conclusion

@@
 date: 20 January 2024
+thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/Sta302_Major_Crime_Indicators"
 abstract: "Safety is one of the most important factors that people consider when deciding where to live and go.
@@
 format: pdf
+toc: true
+number-sections: true
 bibliography: references.bib
 ---
-## Introduction
+# Introduction
 On Dec 25th, 2023, the Christmas Day, a news has raised huge concerns among people — a man was seriously injured after stabbing in downtown Toronto.
@@
 
-## Data
+# Data
 
-### Data Source and Software
+## Data Source and Software
 The data utilized throughout this paper, in csv format, was obtained from Toronto Police Services on the City of Toronto Open Data Website [@rOpenDataToronto], with the title “MAJOR CRIME INDICATORS”.
@@
 
-### Data Collection
+## Data Collection
 The dataset contains all Major Crime Indicators occurrences by report data.
@@
 
-### Data Analysis and Visualizations
+## Data Analysis and Visualizations
 The Major Crimes in Toronto dataset contains 27 columns and 372899 rows, including the repeated occurrences with different crime categories.
@@
 There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
-I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other.
+I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other, as shown in Table 2.Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
+North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
 ```{r}
@@
 
-clean_mci_data%>%
-  group_by(division_area) %>%
+clean_mci_data |>
+  group_by(division_area) |>
   summarise(division = toString(unique(division))) |> kable()
@@
 
-Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
-North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
-
 ```{r}
@@
 ```{r}
+#| include: false
 # Share
@@
 
-## Conclusion
+\newpage
+# Conclusion
 In summary, ‘Assault’ has always ranked as the most common major crime over the past ten years.
@@
 \newpage
-
-## References
+# References

### 2024-01-23 outputs/paper/paper.qmd
Change the structure of the paper

@@
 There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
-I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other, as shown in Table 2.Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
+I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other, as shown in Table 2.
+Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
 North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
@@
 ```
+\newpage
 Figure 3 indicates the preferred time to commit crimes.
@@
 
-\newpage
 # Conclusion

### 2024-01-23 script/01-download_data.qmd
Change the typo in scripts

--- 2024-01-21 scripts/01-download_data.qmd
@@
 #### Preamble ####
+# Acquire
 # Purpose: Download and save the actual data on major crimes that reported in Toronto 

### 2024-01-24 scripts/00-simulated_data.R
simulated data and downloaded data change from qmd to R

@@ -1,60 +1,39 @@
----
-title: "Simulated Data for the Analysis of Major Crimes in Toronto"
-author: "Boxuan Yi"
-format: pdf
----
-
-
-```{r}
-#| message: false
-#| echo: false
-#### Preamble ####
 # Purpose: Simulate the dataset of major crimes in Toronto
 # Author: Boxuan Yi
 # Email: boxuan.yi@mail.utoronto.ca
 # Date: 17 January 2024
-```
 
-```{r}
-#| message: false
-#| echo: false
-# Plan
+install.packages('opendatatoronto')
+install.packages('dplyr')
+install.packages('tidyverse')
+install.packages('janitor')
+install.packages('leaflet')
+install.packages('ggplot2')
+install.packages('knitr')
+install.packages('here')
+
 library(tidyverse)
 library(janitor)
-
-```
 
 # Plan
 ![Plan Image](project/scripts/plan.png)
 
 
-
-```{r}
 # Simulate
-#| message: false
-#| echo: false
 # Simulation for the number of crimes in each year (2014-2023) and the month with the most crimes in each year
 set.seed(7)
-
 months <- c("January", "February", "March", "April", "May", "June", "July",
             "August", "September", "October", "November", "December")
-
 simulated_data1 <-
   tibble(
     "Year" = 2014:2023,
     "Number of Crimes" = runif(n = 10, min = 0, max = 10000),
     "Month" = sample(months, 10, replace = TRUE)
-    )
+  )
 simulated_data1
 
-```
-
-```{r}
-#| message: false
-#| echo: false
 # Simulation for the number of crimes classified in major crime types
 set.seed(7)
-
 simulated_data2 <-
   tibble(
     "Year" = 2014:2023,
@@ -63,14 +42,9 @@ simulated_data2 <-
     "Number of Break and Enter" = runif(n = 10, min = 0, max = 2000),
     "Number of Robbery" = runif(n = 10, min = 0, max = 2000),
     "Number of Theft Over" = runif(n = 10, min = 0, max = 2000)
-    )
+  )
 simulated_data2
 
-```
-
-```{r}
-#| message: false
-#| echo: false
 # Simulation for the number of crimes classified in major crime types
 set.seed(7)
 simulated_data3 <-
@@ -82,20 +56,14 @@ simulated_data3 <-
     "Other" = runif(n = 10, min = 0, max = 1000),
[…]

### 2024-01-24 scripts/01-download_data.R

@@ -1,11 +1,3 @@
----
-title: "Download and Save the Actual Data on MCI"
-author: "Boxuan Yi"
-format: html
----
-
-```{r}
-#### Preamble ####
 # Acquire
 # Purpose: Download and save the actual data on major crimes that reported in Toronto 
 # from 2014 to 2023
@@ -14,65 +6,35 @@ format: html
 # Date: 18 January 2024
 # Prerequisites: Know where to get major crimes data.
 # I will use MCI as an abbreviation of Major Crime Indicator
-```
 
-```{r}
-# Install all the packages I need for this analysis
-install.packages('opendatatoronto')
-install.packages('dplyr')
-install.packages('tidyverse')
-install.packages('janitor')
-install.packages('leaflet')
-install.packages('ggplot2')
-install.packages('knitr')
-install.packages('here')
-```
-
-```{r}
 library(opendatatoronto)
 library(dplyr)
 library(tidyverse)
 library(here)
 library(janitor)
-```
 
-```{r}
 # get package and all resources for this package
 package <- show_package("major-crime-indicators")
 resources <- list_package_resources("major-crime-indicators")
-
-# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
 datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
+raw_mci_data <- filter(datastore_resources, row_number()==2) |> get_resource()
 
-# load the second one
-raw_mci_data <- filter(datastore_resources, row_number()==2) %>% get_resource()
-```
-
-```{r}
 # Write data
 write_csv (
   x = raw_mci_data,
   file = "unedited_data.csv"
 )
-```
 
-```{r}
 # Read and clean the dataset
 raw_mci_data <- read_csv(
-    file = here("inputs/data/unedited_data.csv"))
+  file = here("inputs/data/unedited_data.csv"))
 clean_mci_data <- clean_names(raw_mci_data)
-```
 
-```{r}
 # Write the cleaned dataset
 write_csv (
   x = clean_mci_data,
   file = "clean_mci.csv"
 )
-```
 
-```{r}
 clean_mci_data <- read_csv(
-    file = here("inputs/data/clean_mci.csv"))
-```
-
+  file = here("inputs/data/clean_mci.csv"))

### 2024-01-24 outputs/paper/paper.qmd
Improve a few sentences

@@
 author: "Boxuan Yi"
-date: 20 January 2024
-thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/Sta302_Major_Crime_Indicators"
+date: 22 January 2024
+thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/Analysis_of_Major_Crime_Indicators"
 abstract: "Safety is one of the most important factors that people consider when deciding where to live and go.
@@
 ---
+
+\newpage
 # Introduction
@@
   geom_line() +
-  theme(legend.position = "top") +
+  theme(legend.position = "right") +
   labs(x = "Time In a Day", y = "Number of Crimes", color = "Weekday or Weekend") +

### 2024-01-24 scripts/00-simulated_data.R

@@ -2,6 +2,7 @@
 # Author: Boxuan Yi
 # Email: boxuan.yi@mail.utoronto.ca
 # Date: 17 January 2024
+# There are four simulations
 
 install.packages('opendatatoronto')
 install.packages('dplyr')
@@ -14,13 +15,15 @@ install.packages('here')
 
 library(tidyverse)
 library(janitor)
+library(knitr)
 
 # Plan
-![Plan Image](project/scripts/plan.png)
+cat("![My plan](project/scripts/plan.png)\n")
 
 
 # Simulate
-# Simulation for the number of crimes in each year (2014-2023) and the month with the most crimes in each year
+# Simulation for the number of crimes in each year (2014-2023),
+# and the month with the most crimes in each year
 set.seed(7)
 months <- c("January", "February", "March", "April", "May", "June", "July",
             "August", "September", "October", "November", "December")

### 2024-01-25 outputs/paper/paper.qmd
Change and move some content

@@
 ---
-title: "Analysis of Major Crimes in Toronto And Suggestions on How to Protect Ourselves"
+title: "Analysis of Major Crimes in Toronto And Strategies for Safety Amidst Increasing Numbers"
 author: "Boxuan Yi"
@@
 abstract: "Safety is one of the most important factors that people consider when deciding where to live and go.
-This report uses data from Open Data Toronto to analyze the occurrences of various types of crimes in different regions and time of Toronto, as well as the trend over the past ten years.
-The result shows that Downtown Toronto and evenings & noon have a relatively high occurrences of crimes, which could be used as a suggestion on both individual and government dicision-making."
+This paper uses open-access data to analyze the occurrences of various types of crimes in Toronto and their trends over the past ten years.
+Crimes are classified based on regions where they happen and the times when they occur to further analyze the safety issue.
+The result shows that Downtown Toronto and evenings & noon have relatively high occurrences of crimes, which could be used as suggestions for both individual and government decision-making."
 format: pdf
@@
 
-Major crimes statistics is an important tool for resource allocation and law enforcement strategy.
+“Crime is a complicated topic and there are few easy answers.” [@newark2011canadian] Major crimes statistics is an important tool for resource allocation and law enforcement strategy.
 It also provides the public a clear picture of the safety and helps individuals make informed decisions, influencing choices such as when to go out and where to buy a house.
@@
 ## Data Collection
-The dataset contains all Major Crime Indicators occurrences by report data.
+The dataset contains all Major Crime Indicators occurrences by report date.
 The categories of major crimes are Assault, Break and Enter, Auto Theft, Robbery and Theft Over.
@@
 The Major Crimes in Toronto dataset contains 27 columns and 372899 rows, including the repeated occurrences with different crime categories.
-All the samples of major crimes were reported from 2014 to 2023.
-Among 27 columns, the variables I will use are x_id, report_year, occ_year, occ_month, occ_dow (Day of the Week Offence Occurred), occ_hour, mci_category, division.
-I will create two more variables, division_area, which classifies 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA), and weekend_weekday, which indicates whether the occurrence happen on a weekday or a weekend.
+All the samples of major crimes were reported from 2014 to 2023, and each sample includes ID, report time, occurrence time, police division, location type,  neighbourhood, and premise type.
+Among 27 columns, the variables I will use are x_id, report_year, occ_year, occ_month, occ_dow (day of the week offence occurred), occ_hour, mci_category and division.
+I will create two more variables, division_area, which put 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA), and weekend_weekday, which indicates whether the occurrence happen on a weekday or a weekend.
 
@@
 #| label: tbl-clean_mci_data
-#| tbl-cap: The Number of Major Crimes and the Month with the Most Crimes (2014-2023)
+#| tbl-cap: The Number of Major Crimes occurred and the Month with the Most Crimes (2014-2023)
 # Create a table with year, 2014 to 2023, the number of crimes in each year, and the month with the most crimes correspondingly.
@@
 ```
-Table 1 provides a brief summary of the total number of crimes from 2014 to 2023.
+Table 1 @ref(tbl-clean_mci_data) provides a brief summary of the total number of crimes from 2014 to 2023.
 Over this period, the overall number of crimes shows a consistent increase, except for the years 2020 and 2021, which have a decline probably due to the impact of the pandemic.
@@
 
-Figure 1 visualizes the annual distribution of major crime types with five categories: Assault, Break and Enter, Auto Theft, Robbery, and Theft Over.
+Figure 1 @ref(fig-types_of_crimes) visualizes the annual distribution of major crime types with five categories: Assault, Break and Enter, Auto Theft, Robbery, and Theft Over.
 Across all years, 'Assault' records the highest count, followed by 'Break and Enter' and 'Auto Theft'.
@@
 There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
-I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other, as shown in Table 2.
-Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
+I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other as shown in Table 2 @ref(tbl-division_area).
+Based on Figure 2 @ref(fig-area_of_crimes), Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
 North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
+It is crucial to recognize that, though Toronto-East York records the most crimes, it also has the largest number of residents.
+Therefore, it could be biased to claim that Toronto-East York has the highest crime rate, or North York is getting dangerous, as North York has witnessed a growing population in recent years.
+Moreover, when creating this dataset, one occurrence number may have a few rows with different major crime indicators types used to categorize the occurrence.
+Therefore, some incidents of 'Auto Theft,' 'Robbery,' and 'Theft Over' may be potentially recorded multiple times under 'Break and Enter.' Consequently, the number of crimes classified as just ‘Break and Enter’ is overestimated, the actual number may be lower than what is shown now in the dataset.
 ```{r}
@@
 #| label: tbl-division_area
-#| tbl-cap: Police divisions in 6 areas(including other)
+#| tbl-cap: Police divisions classified into six areas (including other)
 
@@
 #| label: fig-area_of_crimes
-#| fig-cap: Total Number of Crimes in Different Police Division Areas
+#| fig-cap: Total Number of Crimes Occurred in Different Police Division Areas (2014-2023)
 clean_mci_data |>
@@
        y = "Total Number of Crimes",
-       color = "Division Area")
+       color = "Division Area")+
+  scale_x_continuous(breaks = seq(2014, 2023, by = 1))
 ```
@@
 #| label: fig-time_of_crimes
-#| fig-cap: Number of Crimes in a Day
+#| fig-cap: Total Number of Crimes Occurred in a Day
 clean_mci_data |>
@@
   labs(x = "Time In a Day", y = "Number of Crimes", color = "Weekday or Weekend") +
-  scale_color_manual(values = c("Weekday" = "steelblue3", "Weekend" = "indianred3"))
+  scale_color_manual(values = c("Weekday" = "steelblue3", "Weekend" = "indianred3"))+
+  scale_x_continuous(breaks = seq(0, 23, by = 1))
 ```
-\newpage
-Figure 3 indicates the preferred time to commit crimes.
+
+Figure 3 @ref(fig-time_of_crimes) indicates the preferred time to commit crimes.
 The graph reveals a higher likelihood of criminal behaviours during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning.
 Interestingly, there is a surprising local peak at noon, while 11:00 and 13:00 do not show a high probability.
+
+The dataset named “Police Annual Statistical Report - Reported Crimes” from OpenDataToronto also provided crime data, including crime id, report_year, division, category, subtype and count.
+However, it overlaps with the information available in “Major Crime Indicators” dataset.
+Given that “Major Crime Indicators” contains more detailed records, I only used “Major Crime Indicators” in this paper.
 
@@
 
-# Conclusion
+## Conclusion
 In summary, ‘Assault’ has always ranked as the most common major crime over the past ten years.
@@
 Focus on safety during midnight and noon hours is important too.
-The most common time for a crime occurrence include noon and midnight, especially between 6:00 PM to 8:00 PM.
+The most common time for a crime occurrence include noon and midnight, especially between 6:00 PM to 23:00 PM.
 In order to prevent such incidents, people who work from home but go out for lunch, as well as those with children returning home for lunch around noon, should keep their ears and eyes open for suspicious surroundings.
@@
 
-It is crucial to recognize that, though Toronto-East York records the most crimes, it also has the largest number of residents.
-Therefore, it could be biased to claim that Toronto-East York has the highest crime rate, or North York is getting dangerous, as North York has witnessed a growing population in recent years.
-Moreover, when creating this dataset, one occurrence number may have a few rows with different major crime indicators types used to categorize the occurrence.
-Therefore, some incidents of 'Auto Theft,' 'Robbery,' and 'Theft Over' may be potentially recorded multiple times under 'Break and Enter.' Consequently, the number of crimes classified as just ‘Break and Enter’ is overestimated, the actual number may be lower than what is shown now in the dataset.
-
 \newpage

### 2024-01-25 scripts/00-simulated_data.R

@@ -4,6 +4,7 @@
 # Date: 17 January 2024
 # There are four simulations
 
+# Install all the packages I need
 install.packages('opendatatoronto')
 install.packages('dplyr')
 install.packages('tidyverse')
@@ -19,7 +20,6 @@ library(knitr)
 
 # Plan
 cat("![My plan](project/scripts/plan.png)\n")
-
 
 # Simulate
 # Simulation for the number of crimes in each year (2014-2023),

### 2024-01-25 scripts/01-download_data.R

@@ -13,7 +13,7 @@ library(tidyverse)
 library(here)
 library(janitor)
 
-# get package and all resources for this package
+# Get package and all resources for this package
 package <- show_package("major-crime-indicators")
 resources <- list_package_resources("major-crime-indicators")
 datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
@@ -38,3 +38,13 @@ write_csv (
 
 clean_mci_data <- read_csv(
   file = here("inputs/data/clean_mci.csv"))
+
+# Test
+clean_mci_data$report_year |> min() == 2014
+clean_mci_data$report_year |> max() == 2023
+clean_mci_data$occ_year |> unique()
+any(duplicated(clean_mci_data$x_id))
+clean_mci_data$mci_category |> unique() == c("Assault", "Robbery", "Auto Theft", "Break and Enter", "Theft Over")
+clean_mci_data$division |> unique()
+clean_mci_data$occ_dow |> unique()
+clean_mci_data$occ_hour |> class() == "numeric"

### 2024-01-25 outputs/paper/paper.qmd
Add some details

@@
 
-“Crime is a complicated topic and there are few easy answers.” [@newark2011canadian] Major crimes statistics is an important tool for resource allocation and law enforcement strategy.
+“Crime is a complicated topic and there are few easy answers [@newark2011canadian]." Major crimes statistics is an important tool for resource allocation and law enforcement strategy.
 It also provides the public a clear picture of the safety and helps individuals make informed decisions, influencing choices such as when to go out and where to buy a house.
@@
 The dataset will be processed and analyzed in R [@r] using packages Dplyr [@rDplyr], Tidyverse [@rTidyverse], Here [@rHere], Leaflet [@rLeaflet], and Janitor [@rJanitor].
-Visualizations including tables and figures will be created using ggplot2 [@rGgplot2] and Knitr[@Knitr].
+Visualizations including tables and figures will be created using ggplot2 [@rGgplot2] and Knitr[@rKnitr].
 
@@
 
-## Data Analysis and Visualizations
+## Data Visualizations and Analysis 
 The Major Crimes in Toronto dataset contains 27 columns and 372899 rows, including the repeated occurrences with different crime categories.
@@
 ```
-Table 1 @ref(tbl-clean_mci_data) provides a brief summary of the total number of crimes from 2014 to 2023.
+@tbl-clean_mci_data provides a brief summary of the total number of crimes from 2014 to 2023.
 Over this period, the overall number of crimes shows a consistent increase, except for the years 2020 and 2021, which have a decline probably due to the impact of the pandemic.
@@
 
-Figure 1 @ref(fig-types_of_crimes) visualizes the annual distribution of major crime types with five categories: Assault, Break and Enter, Auto Theft, Robbery, and Theft Over.
+@fig-types_of_crimes visualizes the annual distribution of major crime types with five categories: Assault, Break and Enter, Auto Theft, Robbery, and Theft Over.
 Across all years, 'Assault' records the highest count, followed by 'Break and Enter' and 'Auto Theft'.
@@
 There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
-I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other as shown in Table 2 @ref(tbl-division_area).
-Based on Figure 2 @ref(fig-area_of_crimes), Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
+I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other as shown in @tbl-division_area.
+Based on @fig-area_of_crimes, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
 North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two.
@@
 
-Figure 3 @ref(fig-time_of_crimes) indicates the preferred time to commit crimes.
+@fig-time_of_crimes indicates the preferred time to commit crimes.
 The graph reveals a higher likelihood of criminal behaviours during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning.

### 2024-01-25 scripts/00-simulated_data.R
Add some descriptions for simulations

@@ -1,7 +1,7 @@
 # Purpose: Simulate the dataset of major crimes in Toronto
 # Author: Boxuan Yi
 # Email: boxuan.yi@mail.utoronto.ca
-# Date: 17 January 2024
+# Date: 22 January 2024
 # There are four simulations
 
 # Install all the packages I need
@@ -22,8 +22,10 @@ library(knitr)
 cat("![My plan](project/scripts/plan.png)\n")
 
 # Simulate
-# Simulation for the number of crimes in each year (2014-2023),
-# and the month with the most crimes in each year
+# Simulation for the number of crimes in each year (2014-2023), and the month with the most crimes in each year
+# It gives a table with 10 rows, and 3 variables: Year (2014-2023), Number of Crimes and Month with the most crimes each year.
+# The number of crimes is randomly chosen using uniform distribution from 0 to 10000.
+# Month is randomly chosen 10 times with replacement
 set.seed(7)
 months <- c("January", "February", "March", "April", "May", "June", "July",
             "August", "September", "October", "November", "December")
@@ -31,11 +33,13 @@ simulated_data1 <-
   tibble(
     "Year" = 2014:2023,
     "Number of Crimes" = runif(n = 10, min = 0, max = 10000),
-    "Month" = sample(months, 10, replace = TRUE)
-  )
+    "Month with the most crimes" = sample(months, 10, replace = TRUE)
+  ) |> kable()
 simulated_data1
 
 # Simulation for the number of crimes classified in major crime types
+# It gives a table with years (2014 to 2023) and numbers of crimes for 5 types of crime
+# Numbers of crimes are randomly chosen using uniform distribution from 0 to 2000.
 set.seed(7)
 simulated_data2 <-
   tibble(
@@ -45,10 +49,12 @@ simulated_data2 <-
     "Number of Break and Enter" = runif(n = 10, min = 0, max = 2000),
     "Number of Robbery" = runif(n = 10, min = 0, max = 2000),
     "Number of Theft Over" = runif(n = 10, min = 0, max = 2000)
-  )
+  ) |> kable()
 simulated_data2
 
 # Simulation for the number of crimes classified in major crime types
+# It gives a table with years (2014 to 2023) and numbers of crimes for 6 different regions
+# Numbers of crimes are randomly chosen using uniform distribution from 0 to 1000.
 set.seed(7)
[…]

### 2024-01-25 scripts/01-download_data.R
Modify test and date

@@ -3,7 +3,7 @@
 # from 2014 to 2023
 # Author: Boxuan Yi
 # Email: boxuan.yi@mail.utoronto.ca
-# Date: 18 January 2024
+# Date: 22 January 2024
 # Prerequisites: Know where to get major crimes data.
 # I will use MCI as an abbreviation of Major Crime Indicator
 

### 2024-01-25 outputs/paper/paper.qmd
Final check and correct typo

@@
 # Explore
-# Test
+# Tests
 clean_mci_data$report_year |> min() == 2014
@@
 #| tbl-cap: The Number of Major Crimes occurred and the Month with the Most Crimes (2014-2023)
-# Create a table with year, 2014 to 2023, the number of crimes in each year, and the month with the most crimes correspondingly.
+# Create a table with years, 2014 to 2023, the number of crimes in each year, and the month with the most crimes correspondingly.
 clean_mci_data |>
@@
 #| fig-cap: The Number of Crimes Reported, Classified by Crime Types (2014-2023)
+# Create a histogram with numbers of crimes classified by crime types from 2014 to 2023
 clean_mci_data |>
@@
 #| include: false
+# Create a new variable division_area, which put 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA)
 clean_mci_data <- clean_mci_data |>
@@
 #| include: false
+# Create a new variable weekend_weekday, which indicates whether the occurrence happen on a weekday or a weekend
 clean_mci_data <- clean_mci_data |> 
@@
 There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
-I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other as shown in @tbl-division_area.
+I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York and other, as shown in @tbl-division_area.
 Based on @fig-area_of_crimes, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
@@
 #| tbl-cap: Police divisions classified into six areas (including other)
-
+# Create a table to show the realation between the new variable division_area and division
 clean_mci_data |>
@@
 #| fig-cap: Total Number of Crimes Occurred in Different Police Division Areas (2014-2023)
+# Visualize the number of crimes occurred in different police division areas
 clean_mci_data |>
@@
 #| fig-cap: Total Number of Crimes Occurred in a Day
+# Create a line chart showing the total number of crimes occurred in 24 hours in a day
 clean_mci_data |>

### 2024-01-25 scripts/01-download_data.R

@@ -39,7 +39,7 @@ write_csv (
 clean_mci_data <- read_csv(
   file = here("inputs/data/clean_mci.csv"))
 
-# Test
+# Tests
 clean_mci_data$report_year |> min() == 2014
 clean_mci_data$report_year |> max() == 2023
 clean_mci_data$occ_year |> unique()

### 2024-01-25 outputs/paper/paper.qmd
Correct grammar mistakes

@@
 # Introduction
-On Dec 25th, 2023, the Christmas Day, a news has raised huge concerns among people — a man was seriously injured after stabbing in downtown Toronto.
-This was not the first such incident on that block in December; unfortunately, such distressing news has become more and more prevalent nowadays.
-As the pandemic comes to an end, there is a noticeable increase in people returning to the office and going out more frequently than in previous years.
-Naturally, public safety and private security have become particularly crucial, leading to a significant question: How can we proactively prevent such incidents from affecting ourselves and our loved ones?
+On December 25th, 2023, Christmas Day, an incident raised significant concerns among people — a man was seriously injured after a stabbing in downtown Toronto.
+This was not the first occurrence on that block in December; Unfortunately, such distressing news has become increasingly prevalent nowadays.
+As the pandemic comes to an end, there is a noticeable increase in people returning to the office and engaging in more regular social activities compared to previous years.
+Naturally, public and personal safety has become particularly crucial, leading to a significant question: How can we proactively prevent such incidents from affecting ourselves and our loved ones?
 
 “Crime is a complicated topic and there are few easy answers [@newark2011canadian]." Major crimes statistics is an important tool for resource allocation and law enforcement strategy.
-It also provides the public a clear picture of the safety and helps individuals make informed decisions, influencing choices such as when to go out and where to buy a house.
+It also provides the public a clear picture of the safety and empowers individuals to make informed decisions, influencing choices such as when to go out and where to buy a house.
 For this paper, I will use open-access data, titled ‘Major Crime Indicator’ from the OpenDataToronto [@rOpenDataToronto] to analyze the distribution of major crimes—classified as Assault, Break and Enter, Auto Theft, Robbery, and Theft Over—over the past ten years.
@@
 There are two factors that may influence the reliability of the data.
-First, this dataset includes all occurrences reported to the Toronto Police Station, except those have been considered as unfounded.
-Second, this data is provided at the offence and victim level, so one occurrence number may have a few rows of data with different major crime indicators types used to categorize the occurrence.
+First, this dataset includes all occurrences reported to the Toronto Police Station, except those that have been considered as unfounded.
+Second, this data is provided at the offence and victim level, so one occurrence number may have a few rows of data with different major crime indicator types used to categorize the occurrence.
 
@@
 The Major Crimes in Toronto dataset contains 27 columns and 372899 rows, including the repeated occurrences with different crime categories.
-All the samples of major crimes were reported from 2014 to 2023, and each sample includes ID, report time, occurrence time, police division, location type,  neighbourhood, and premise type.
+All major crime samples were reported between 2014 and 2023, and each sample includes ID, report time, occurrence time, police division, location type,  neighbourhood, and premise type.
 Among 27 columns, the variables I will use are x_id, report_year, occ_year, occ_month, occ_dow (day of the week offence occurred), occ_hour, mci_category and division.
-I will create two more variables, division_area, which put 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA), and weekend_weekday, which indicates whether the occurrence happen on a weekday or a weekend.
+I will create two more variables, division_area, which puts 18 police divisions (including a NSA) into 6 regions of Toronto (including Other for NSA), and weekend_weekday, which indicates whether the occurrence happened on a weekday or a weekend.
 
@@
 There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA.
-I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York and other, as shown in @tbl-division_area.
+I have grouped them into six geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York and other, as illustrated in @tbl-division_area.
 Based on @fig-area_of_crimes, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest.
@@
 It is crucial to recognize that, though Toronto-East York records the most crimes, it also has the largest number of residents.
-Therefore, it could be biased to claim that Toronto-East York has the highest crime rate, or North York is getting dangerous, as North York has witnessed a growing population in recent years.
+Therefore, asserting that Toronto-East York has the highest number or that North York is becoming more dangerous might be biased, as North York has witnessed a growing population in recent years.
 Moreover, when creating this dataset, one occurrence number may have a few rows with different major crime indicators types used to categorize the occurrence.
@@
 @fig-time_of_crimes indicates the preferred time to commit crimes.
-The graph reveals a higher likelihood of criminal behaviours during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning.
-Interestingly, there is a surprising local peak at noon, while 11:00 and 13:00 do not show a high probability.
+The graph reveals a higher likelihood of criminal behaviours during the evening, with occurrences steadily increasing as the night progresses towards midnight.
+Afterwards, the occurrences decrease until six in the morning.
+Interestingly, there is a surprising local peak at noon, while 11:00 and 13:00 do not show a high number.
 
-The dataset named “Police Annual Statistical Report - Reported Crimes” from OpenDataToronto also provided crime data, including crime id, report_year, division, category, subtype and count.
+The dataset named “Police Annual Statistical Report - Reported Crimes” from OpenDataToronto also provides crime data, including crime id, report_year, division, category, subtype and count.
 However, it overlaps with the information available in “Major Crime Indicators” dataset.
